Visual Diagnostics for Constrained Optimisation with Application to Guided Tours

### 2021-01-31 paper/zhang-cook-laa-langrene-menendez.tex
add the plot for the orientation section

\hypertarget{flipping-the-sign-in-the-bases}{%
\subsection{Flipping the sign in the
bases}\label{flipping-the-sign-in-the-bases}}

>>>>

\hypertarget{reconciling-the-orientation}{%
\subsection{Reconciling the
orientation}\label{reconciling-the-orientation}}

\begin{Schunk}
\begin{figure}
\includegraphics[width=1\linewidth]{/Users/hzha400/Documents/PhD/research/paper-tour-vis/figs/flip-sign-1} \caption[PCA plot of 1D projection of boa6 data, optimised by SA, with seed 2463]{PCA plot of 1D projection of boa6 data, optimised by SA, with seed 2463.}\label{fig:flip-sign}
\end{figure}
\end{Schunk}
